Tables and Figures - Supplement A, B and C

### 2019-12-11 code/06_Supplement-tables-figures.Rmd
Dropped table from Supplement A

---
title: "Tables and Figures - Supplement A and B"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

This document contains the code to reproduce tables and figures from Supplement A and Supplement B for the project "Heterogeneity in direct replications in psychology and its association with effect size".

@@

## Supplement A

@@

#Table S1A.
###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, cache = TRUE}
#library(metafor)
#library(dplyr)
#library(purrr)

#fit a random effects model to all empirical data
#Each set of input datapoints is meta-analyzed as per the original replication project
#Function 'est_heterogen_smd_raw' is sourced
res <- dat %>%
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
  mutate(tau = sqrt(tau2),
         tau_ci.lb = sqrt(tau2_ci.lb),
         tau_ci.ub = sqrt(tau2_ci.ub)) %>%
  select(-tau2, - tau2_ci.lb, -tau2_ci.ub) #drop redundant variables

#Transform effect sizes to biserial correlations (pearson's correlations left as is)
#estimate tau2 for correlations
#'transform_MA' and 'summarizer' are sourced functions
res2 <- dat %>%
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map(transform_MA) %>% #
  map_dfr(summarizer, .id = "effect")

res <- res %>%
  mutate(r = res2$r,
         tau_r = sqrt(res2$tau2), #For table 3, report tau and transformed effect sizes (biserial correlations)
         tau_r_ci.lb = sqrt(res2$tau2.lb),
         tau_r_ci.ub = sqrt(res2$tau2.ub))

#Add rp and k to the data-frame and prep for table
het <- dat %>%
  select(rp, Site, effect, effect_type) %>%
  group_by(rp, effect) %>%
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>%
  left_join(res) %>%
  mutate(effect_type = recode(effect_type,
                              d = "SMD",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>%
  ungroup()

#Load simulation results (power/type 1 error for all effects)
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

#Summary of simulation results, needs to be combined with main part of table
I2_power <- dens %>%
  bind_rows(.id = "effect") %>%
  group_by(effect, tau_index) %>%
  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
  ungroup() %>%
  tidyr::spread(key = tau_index, value = power) %>% #prep for table
  rename(zero = '1', small = '2', medium = '3', large = '4')

#Combine dataframes to create full table
het <-  het %>%
  left_join(I2_power) %>%
  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by I2 and upper CI bound
  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 1), nsmall = 1)), ", ", trimws(format(round(s_ci.ub, 1), nsmall = 1)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
         s_I2 = format(round(s_I2, 1), nsmall = 1),
         tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_ci.ub, 3), nsmall = 3)), "]"),
         tau = format(round(tau, 3), nsmall = 3),
         tau_r = format(round(tau_r, 3), nsmall = 3),
         tau_r_ci = paste0("[", trimws(format(round(tau_r_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_r_ci.ub, 3), nsmall = 3)), "]")) %>% #rounded here instead of in table function because should have 4 digits
  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, tau, tau_ci, r, tau_r, tau_r_ci, zero, small, medium, large)

```{r heterogeneity-table, cache = FALSE}
#library(kableExtra)

het %>% knitr::kable(align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau$", "$\\tau$ 95\\% CI", "r*" , "r* $\\tau$", "r* $\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
  add_header_above(c(" " = 12, "Level of heterogeneity" = 4)) %>%
  add_header_above(c(" " = 12, "Type I Error Rate & Statistical Power" = 4)) %>%
  kable_styling("scale_down", font_size = 7) %>% #comment out if outputting html file
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, K = no. primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations. $I^2$ and its confidence intervals are for original effect size specifications whereas $\tau$ and its confidence intervals are for transformed r* effect sizes. Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: https://osf.io/j9zyd/?view\\\\_only=e6639d8d4f924739a7310782fbbb4e06",
           alphabet = "These effects were simulated as standardized mean differences") %>%
  landscape()

## Supplement B

@@

@@

```{r}
knitr::kable(comparison, digits = 2)
```

@@

## Supplement C

@@

Table S1C. The Pearson correlations from 40 meta-analyses estimated with the random effects model and restricted maximum likelihood. $s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis. This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless. In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences. Effects reported as mean differences were standardized for the meta-analyses.

@@

Table S2C. The Pearson correlations from 36 meta-analyses estimated with the random effects model and restricted maximum likelihood. The sample of effects is identical to Table S1C but with 4 Anchoring effects excluded. $s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis. This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless. In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences. Effects reported as mean differences were standardized for the meta-analyses.

@@

>>>>

---
title: "Tables and Figures - Supplement A, B and C"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

This document contains the tables and figures from Supplement A, B and C for the project "Heterogeneity in direct replications in psychology and its association with effect size".

@@

# Supplement A

@@

# Supplement B

@@

## Table S1B

@@

```{r}
knitr::kable(comparison, digits = 2, longtable = TRUE, booktabs = TRUE) %>% 
  add_header_above(c(" " = 1, "True effect size zero" = 4, "True effect size medium" = 4)) %>% 
  add_header_above(c(" " = 1, "Type I error rate and power for different heterogeneity levels" = 8))
```

@@

# Supplement C

@@

## Table S1C.

@@

**Note:** The Pearson correlations from 40 meta-analyses estimated with the random effects model and restricted maximum likelihood. $s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis. This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless. In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences. Effects reported as mean differences were standardized for the meta-analyses.

## Table S2C.

@@

**Note:** The Pearson correlations from 36 meta-analyses estimated with the random effects model and restricted maximum likelihood. The sample of effects is identical to Table S1C but with 4 Anchoring effects excluded. $s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis. This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless. In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences. Effects reported as mean differences were standardized for the meta-analyses.
